\speculake: Hiding Malware in Speculative Execution

### 2018-08-02 paper/discussion.tex
move redpils to discussion

>>>>

\paragraph{Red-Pills}
Hardware minutia have also been used to identify and fingerprint execution
environments---in malware this is known as a red-pill~\cite{red-pill} and is
typically used by malware to detect when it is under emulation or a debugging
environment~\cite{lindorfer2011detecting, balzarotti2010efficient,
paleari2009fistful} attempting to circumvent malware detectors. To address
red-pills, systems often employ measures to detect them. ``Bare-metal''
emulation of malware~\cite{kirat2011barebox}, methods to determine if malware is
performing red-pill checks to avoid emulation
environments~\cite{kirat2014barecloud}, and symbolic execution can be used to
combat red-pills by finding environmental triggers in malicious
binaries~\cite{schwartz2010all}.

Analogously, \speculake undertakes to avoid detection. Unlike previous
red-pills, \speculake complicates analysis and impedes malware detectors with
the use a trigger program and speculative execution. The use of a separate and
seemingly benign trigger program influenced by the adversary enables the
\speculake malware to limit detection by acting benign until triggered to
influence the branch predictor (while still appearing innocuous).

Additionally, as an \speculake attack is carried out via speculative execution,
the instructions executed and speculative state are not committed to by the
processor and are thus obscured from analysts. Similarly, symbolic execution
will fail to find the speculative gadgets as they are never on the (committed)
execution pathway. More direct analysis such as with break-points (and other
debugging techniques) will not aid in unravelling \speculake malware as
break-points interrupt the control flow of a program and prevent speculative
execution. This allows \speculake to effectively act as a red-pill while
avoiding detection as such. Suggesting that significant work would be required
to adapt current red-pill detectors to detect \speculake malware.
